Reproductive Allocation Calculations

### 2014-12-19 docs/CarbonInvestments.tex
Document now compiles with new data

\graphicspath{../output/docs}

@@

\begin{document}
\maketitle
\chapter{Software description}
\section{Purpose of software}
The goal of the code is to:
\begin{itemize}
\item Estimate reproductive investment from census data
\item Estimate growth investment
\item Determin Reproductive Allocation schedules for 14 species.
\end{itemize}
\section{Structure of Software}
\begin{center}
\includegraphics[width=0.75\linewidth]{Flow1.png}\\
\includegraphics[width=0.75\linewidth]{Flow2.png}\\
\includegraphics[width=0.75\linewidth]{Flow3.png}
\end{center}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=6in]{PlantGraph.pdf}
\end{center}
\caption{Graphical presentation of the \texttt{igraph} tree structure of plant map for COER.}
\end{figure}

@@

\clearpage
\newpage
\section{BAER}
\begin{multicols}{2}
\includegraphics[width=3in]{BAER.png}
\vfill
\columnbreak
\input{../output/docs/BAER.tex}
\end{multicols}

\clearpage
\newpage
\section{BOLE}
\begin{multicols}{2}
\includegraphics[width=3in]{BOLE.png}
\vfill
\columnbreak
\input{../output/docs/BOLE.tex}
\end{multicols}

@@

\section{COER}
\begin{multicols}{2}
\includegraphics[width=2.7in]{COER.png}
\vfill
\columnbreak
\input{../output/docs/COER.tex}
\end{multicols}

@@

\section{EPMI}
\begin{multicols}{2}
\includegraphics[width=2.5in]{EPMI.png}
\vfill
\columnbreak
\input{../output/docs/EPMI.tex}
\end{multicols}

@@

\section{GRBU}
\begin{multicols}{2}
\includegraphics[width=3in]{GRBU.png}
\vfill
\columnbreak

\input{../output/docs/GRBU.tex}\\

@@

\section{GRSP}
\begin{multicols}{2}
\includegraphics[width=3in]{GRSP.png}
\vfill
\columnbreak

\input{../output/docs/GRSP.tex}

@@

\clearpage
\newpage
\section{HATE}
\begin{multicols}{2}
\includegraphics[width=3in]{HATE.png}
\vfill
\columnbreak
\input{../output/docs/HATE.tex}

@@

\section{HEPU}
\begin{multicols}{2}
\includegraphics[width=3in]{HEPU.png}
\vfill
\columnbreak
\input{../output/docs/HEPU.tex}
\end{multicols}

@@

\section{LEES}
\begin{multicols}{2}
\includegraphics[width=3in]{LEES.png}
\vfill
\columnbreak
%%%%
\input{../output/docs/LEES.tex}
%%%%%
\\
\end{multicols}
\clearpage
\newpage

\section{PELA}
\begin{multicols}{2}
\includegraphics[width=2.8in]{PELA.png}
\vfill
\columnbreak
\input{../output/docs/PELA.tex}
\end{multicols}

\clearpage
\newpage
\section{PEPU}
\begin{multicols}{2}
\includegraphics[width=2.7in]{PEPU.png}
\vfill
\columnbreak
\input{../output/docs/PEPU.tex}
\end{multicols}
\clearpage
\newpage

\clearpage
\newpage
\section{PHPH}
\begin{multicols}{2}
\includegraphics[width=3in]{PHPH.png}
\vfill
\columnbreak
\input{../output/docs/PHPH.tex}
\end{multicols}

\clearpage
\newpage
\section{PILI}
\begin{multicols}{2}
\includegraphics[width=2.7in]{PILI.png}
\vfill
\columnbreak
\input{../output/docs/PILI.tex}
\end{multicols}

\clearpage
\newpage
\section{PUTU}
\begin{multicols}{2}
\includegraphics[width=2.5in]{PUTU.png}
\vfill
\columnbreak
\input{../output/docs/PUTU.tex}
\end{multicols}

@@

\begin{figure}[h!]
\begin{center}
\input{../output/docs/AvCountsPerMM.tex}
\end{center}
\caption{Table summarising the average number of elements per mm. To be used for calculations of mass based on the length for conversion to counts.}
\end{figure}

\section{Regression Fits and Coefficients}
\subsection*{GRBU}
\begin{center}
\includegraphics[width=2.7in]{../output/docs/GRBU_fruit_large_immature.pdf}
\includegraphics[width=2.7in]{../output/docs/GRBU_seed_pod.pdf}
\end{center}

\subsection{GRSP}
\begin{center}
\includegraphics[width=2.7in]{../output/docs/GRSP_fruit_large_immature.pdf}
\includegraphics[width=2.7in]{../output/docs/GRSP_seed_pod.pdf}
\end{center}

\subsection{PELA}
\begin{center}
\includegraphics[width=2.7in]{../output/docs/PELA_fruit_large_immature.pdf}
\includegraphics[width=2.7in]{../output/docs/PELA_seed_pod.pdf}\\
\includegraphics[width=2.7in]{../output/docs/PELA_seed.pdf}
\end{center}

\subsection{BAER}
\begin{center}
\includegraphics[width=2.7in]{../output/docs/BAER_cone_young.pdf}
\includegraphics[width=2.7in]{../output/docs/BAER_cone_green.pdf}\\
\includegraphics[width=2.7in]{../output/docs/BAER_cone_brown_no_expanded_follicles.pdf}
\includegraphics[width=2.7in]{../output/docs/BAER_cone_brown.pdf}\\
\includegraphics[width=2.7in]{../output/docs/BAER_cone_aborted.pdf}
\includegraphics[width=2.7in]{../output/docs/BAER_cone_base_green.pdf}\\
\includegraphics[width=2.7in]{../output/docs/BAER_cone_base_brown.pdf}
\end{center}

\subsection{PEPU}
\begin{center}
\includegraphics[width=2.7in]{../output/docs/PEPU_cone_green.pdf}
\includegraphics[width=2.7in]{../output/docs/PEPU_cone_brown.pdf}\\
\includegraphics[width=2.7in]{../output/docs/PEPU_cone_aborted.pdf}
\end{center}
\newpage
\subsection{Summary table for regression}
\begin{figure}[h!]
\begin{center}
\input{../output/docs/RegressionTable.tex}
\end{center}
\caption{Table summarising the equations used to determine weights of individual plant parts by using their size.}
\end{figure}

\chapter{Preliminary results}
\section{Reproductive allocation results}
\subsection{Overview}
\includegraphics[width=1\linewidth]{../output/docs/RA_comparison.pdf}
\includegraphics[width=1\linewidth]{../output/docs/RA_Diam_comparison.pdf}
\includegraphics[width=1\linewidth]{../output/docs/RA_Weight_comparison.pdf}
\clearpage
\newpage
\section{Individual species}
\subsection{BAER}
\includegraphics[width=1\linewidth]{../output/docs/RA_BAER.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_BAER_DW.pdf}}

\clearpage
\newpage
\subsection{BOLE}
\includegraphics[width=1\linewidth]{../output/docs/RA_BOLE.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_BOLE_DW.pdf}}

\clearpage
\newpage
\subsection{COER}
\includegraphics[width=1\linewidth]{../output/docs/RA_COER.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_COER_DW.pdf}}

\clearpage
\newpage
\subsection{EPMI}
\includegraphics[width=1\linewidth]{../output/docs/RA_EPMI.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_EPMI_DW.pdf}}

\clearpage
\newpage
\subsection{GRBU}
\includegraphics[width=1\linewidth]{../output/docs/RA_GRBU.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_GRBU_DW.pdf}}

\clearpage
\newpage
\subsection{GRSP}
\includegraphics[width=1\linewidth]{../output/docs/RA_GRSP.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_GRSP_DW.pdf}}

\clearpage
\newpage
\subsection{HATE}
\includegraphics[width=1\linewidth]{../output/docs/RA_HATE.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_HATE_DW.pdf}}

\clearpage
\newpage
\subsection{HEPU}
\includegraphics[width=1\linewidth]{../output/docs/RA_HEPU.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_HEPU_DW.pdf}}

\clearpage
\newpage
\subsection{LEES}
\includegraphics[width=1\linewidth]{../output/docs/RA_LEES.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_LEES_DW.pdf}}

\clearpage
\newpage
\subsection{PELA}
\includegraphics[width=1\linewidth]{../output/docs/RA_PELA.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PELA_DW.pdf}}

\clearpage
\newpage
\subsection{PEPU}
\includegraphics[width=1\linewidth]{../output/docs/RA_PEPU.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PEPU_DW.pdf}}

\clearpage
\newpage
\subsection{PHPH}
\includegraphics[width=1\linewidth]{../output/docs/RA_PHPH.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PHPH_DW.pdf}}

\clearpage
\newpage
\subsection{PILI}
\includegraphics[width=1\linewidth]{../output/docs/RA_PILI.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PILI_DW.pdf}}

\clearpage
\newpage
\subsection{PUTU}
\includegraphics[width=1\linewidth]{../output/docs/RA_PUTU.pdf}
\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PUTU_DW.pdf}}

>>>>

@@

\begin{document}
\maketitle
\chapter{Software description}
\section{Purpose of software}
The goal of the code is to:
\begin{itemize}
\item Estimate reproductive investment from census data
\item Estimate growth investment
\item Determin Reproductive Allocation schedules for 14 species.
\end{itemize}
\section{Structure of Software}
\begin{center}
\includegraphics[width=0.75\linewidth]{images/Flow1.png}\\
\includegraphics[width=0.75\linewidth]{images/Flow2.png}\\
\includegraphics[width=0.75\linewidth]{images/Flow3.png}
\end{center}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=6in]{images/PlantGraph.pdf}
\end{center}
\caption{Graphical presentation of the \texttt{igraph} tree structure of plant map for COER.}
\end{figure}

@@

\clearpage
\newpage
\section{BAER}
\begin{multicols}{2}
\includegraphics[width=3in]{images/BAER.png}
\vfill
\columnbreak
\input{tables/BAER.tex}
\end{multicols}

\clearpage
\newpage
\section{BOLE}
\begin{multicols}{2}
\includegraphics[width=3in]{images/BOLE.png}
\vfill
\columnbreak
\input{tables/BOLE.tex}
\end{multicols}

@@

\section{COER}
\begin{multicols}{2}
\includegraphics[width=2.7in]{images/COER.png}
\vfill
\columnbreak
\input{tables/COER.tex}
\end{multicols}

@@

\section{EPMI}
\begin{multicols}{2}
\includegraphics[width=2.5in]{images/EPMI.png}
\vfill
\columnbreak
\input{tables/EPMI.tex}
\end{multicols}

@@

\section{GRBU}
\begin{multicols}{2}
\includegraphics[width=3in]{images/GRBU.png}
\vfill
\columnbreak

\input{tables/GRBU.tex}\\

@@

\section{GRSP}
\begin{multicols}{2}
\includegraphics[width=3in]{images/GRSP.png}
\vfill
\columnbreak

\input{tables/GRSP.tex}

@@

\clearpage
\newpage
\section{HATE}
\begin{multicols}{2}
\includegraphics[width=3in]{images/HATE.png}
\vfill
\columnbreak
\input{tables/HATE.tex}

@@

\section{HEPU}
\begin{multicols}{2}
\includegraphics[width=3in]{images/HEPU.png}
\vfill
\columnbreak
\input{tables/HEPU.tex}
\end{multicols}

@@

\section{LEES}
\begin{multicols}{2}
\includegraphics[width=3in]{images/LEES.png}
\vfill
\columnbreak
%%%%
\input{tables/LEES.tex}
%%%%%
\\
\end{multicols}
\clearpage
\newpage

\section{PELA}
\begin{multicols}{2}
\includegraphics[width=2.8in]{images/PELA.png}
\vfill
\columnbreak
\input{tables/PELA.tex}
\end{multicols}

\clearpage
\newpage
\section{PEPU}
\begin{multicols}{2}
\includegraphics[width=2.7in]{images/PEPU.png}
\vfill
\columnbreak
\input{tables/PEPU.tex}
\end{multicols}
\clearpage
\newpage

\clearpage
\newpage
\section{PHPH}
\begin{multicols}{2}
\includegraphics[width=3in]{images/PHPH.png}
\vfill
\columnbreak
\input{tables/PHPH.tex}
\end{multicols}

\clearpage
\newpage
\section{PILI}
\begin{multicols}{2}
\includegraphics[width=2.7in]{images/PILI.png}
\vfill
\columnbreak
\input{tables/PILI.tex}
\end{multicols}

\clearpage
\newpage
\section{PUTU}
\begin{multicols}{2}
\includegraphics[width=2.5in]{images/PUTU.png}
\vfill
\columnbreak
\input{tables/PUTU.tex}
\end{multicols}

@@

\begin{figure}[h!]
\begin{center}
\input{tables/AvCountsPerMM.tex}
\end{center}
\caption{Table summarising the average number of elements per mm. To be used for calculations of mass based on the length for conversion to counts.}
\end{figure}

% TODO: Include these plots
% \section{Regression Fits and Coefficients}
% \subsection*{GRBU}
% \begin{center}
% \includegraphics[width=2.7in]{figures/GRBU_fruit_large_immature.pdf}
% \includegraphics[width=2.7in]{figures/GRBU_seed_pod.pdf}
% \end{center}

% \subsection{GRSP}
% \begin{center}
% \includegraphics[width=2.7in]{figures/GRSP_fruit_large_immature.pdf}
% \includegraphics[width=2.7in]{figures/GRSP_seed_pod.pdf}
% \end{center}

% \subsection{PELA}
% \begin{center}
% \includegraphics[width=2.7in]{figures/PELA_fruit_large_immature.pdf}
% \includegraphics[width=2.7in]{figures/PELA_seed_pod.pdf}\\
% \includegraphics[width=2.7in]{figures/PELA_seed.pdf}
% \end{center}

% \subsection{BAER}
% \begin{center}
% \includegraphics[width=2.7in]{figures/BAER_cone_young.pdf}
% \includegraphics[width=2.7in]{figures/BAER_cone_green.pdf}\\
% \includegraphics[width=2.7in]{figures/BAER_cone_brown_no_expanded_follicles.pdf}
% \includegraphics[width=2.7in]{figures/BAER_cone_brown.pdf}\\
% \includegraphics[width=2.7in]{figures/BAER_cone_aborted.pdf}
% \includegraphics[width=2.7in]{figures/BAER_cone_base_green.pdf}\\
% \includegraphics[width=2.7in]{figures/BAER_cone_base_brown.pdf}
% \end{center}

% \subsection{PEPU}
% \begin{center}
% \includegraphics[width=2.7in]{figures/PEPU_cone_green.pdf}
% \includegraphics[width=2.7in]{figures/PEPU_cone_brown.pdf}\\
% \includegraphics[width=2.7in]{figures/PEPU_cone_aborted.pdf}
% \end{center}

\newpage
\subsection{Summary table for regression}
\begin{figure}[h!]
\begin{center}
\input{tables/RegressionTable.tex}
\end{center}
\caption{Table summarising the equations used to determine weights of individual plant parts by using their size.}
\end{figure}

\chapter{Preliminary results}
\section{Reproductive allocation results}
\subsection{Overview}
\includegraphics[width=1\linewidth]{figures/RA_comparison_age.pdf}
\includegraphics[width=1\linewidth]{figures/RA_comparison_diam.pdf}
\includegraphics[width=1\linewidth]{figures/RA_comparison_weight.pdf}
\clearpage

TODO:Add this material back in

\newpage
\section{Individual species}
\subsection{BAER}
\includegraphics[width=1\linewidth]{figures/RA_age_BAER.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_BAER.pdf}

\clearpage
\newpage
\subsection{BOLE}
\includegraphics[width=1\linewidth]{figures/RA_age_BOLE.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_BOLE.pdf}

\clearpage
\newpage
\subsection{COER}
\includegraphics[width=1\linewidth]{figures/RA_age_COER.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_COER.pdf}

\clearpage
\newpage
\subsection{EPMI}
\includegraphics[width=1\linewidth]{figures/RA_age_EPMI.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_EPMI.pdf}

\clearpage
\newpage
\subsection{GRBU}
\includegraphics[width=1\linewidth]{figures/RA_age_GRBU.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_GRBU.pdf}

\clearpage
\newpage
\subsection{GRSP}
\includegraphics[width=1\linewidth]{figures/RA_age_GRSP.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_GRSP.pdf}

\clearpage
\newpage
\subsection{HATE}
\includegraphics[width=1\linewidth]{figures/RA_age_HATE.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_HATE.pdf}

\clearpage
\newpage
\subsection{HEPU}
\includegraphics[width=1\linewidth]{figures/RA_age_HEPU.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_HEPU.pdf}

\clearpage
\newpage
\subsection{LEES}
\includegraphics[width=1\linewidth]{figures/RA_age_LEES.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_LEES.pdf}

\clearpage
\newpage
\subsection{PELA}
\includegraphics[width=1\linewidth]{figures/RA_age_PELA.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PELA.pdf}

\clearpage
\newpage
\subsection{PEPU}
\includegraphics[width=1\linewidth]{figures/RA_age_PEPU.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PEPU.pdf}

\clearpage
\newpage
\subsection{PHPH}
\includegraphics[width=1\linewidth]{figures/RA_age_PHPH.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PHPH.pdf}

\clearpage
\newpage
\subsection{PILI}
\includegraphics[width=1\linewidth]{figures/RA_age_PILI.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PILI.pdf}

\clearpage
\newpage
\subsection{PUTU}
\includegraphics[width=1\linewidth]{figures/RA_age_PUTU.pdf}
\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PUTU.pdf}

% \newpage
% \section{Investment in Accessory Tissues}
% \subsection{Overview}
% \includegraphics[width=1\linewidth]{figures/IAT_Comparison.pdf}
% \clearpage
% \newpage
% \section{Individual species}
% \subsection{BAER}
% \includegraphics[width=1\linewidth]{figures/IAT_BAER.pdf}

% \subsection{BOLE}
% \includegraphics[width=1\linewidth]{figures/IAT_BOLE.pdf}

% \subsection{COER}
% \includegraphics[width=1\linewidth]{figures/IAT_COER.pdf}

% \subsection{EPMI}
% \includegraphics[width=1\linewidth]{figures/IAT_EPMI.pdf}

% \subsection{GRBU}
% \includegraphics[width=1\linewidth]{figures/IAT_GRBU.pdf}

% \subsection{GRSP}
% \includegraphics[width=1\linewidth]{figures/IAT_GRSP.pdf}

% \subsection{HATE}
% \includegraphics[width=1\linewidth]{figures/IAT_HATE.pdf}

% \subsection{HEPU}
% \includegraphics[width=1\linewidth]{figures/IAT_HEPU.pdf}

% \subsection{LEES}
% \includegraphics[width=1\linewidth]{figures/IAT_LEES.pdf}

% \subsection{PELA}
% \includegraphics[width=1\linewidth]{figures/IAT_PELA.pdf}

% \subsection{PEPU}
% \includegraphics[width=1\linewidth]{figures/IAT_PEPU.pdf}

% \subsection{PHPH}
% \includegraphics[width=1\linewidth]{figures/IAT_PHPH.pdf}

% \subsection{PILI}
% \includegraphics[width=1\linewidth]{figures/IAT_PILI.pdf}

% \subsection{PUTU}
% \includegraphics[width=1\linewidth]{figures/IAT_PUTU.pdf}
